---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# crowdtangler

<!-- badges: start -->
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://lifecycle.r-lib.org/articles/stages.html#experimental)
[![R-CMD-check](https://github.com/JBGruber/crowdtangler/workflows/R-CMD-check/badge.svg)](https://github.com/JBGruber/crowdtangler/actions)
[![Codecov test coverage](https://codecov.io/gh/JBGruber/crowdtangler/branch/main/graph/badge.svg)](https://codecov.io/gh/JBGruber/crowdtangler?branch=main)
[![Twitter](https://img.shields.io/twitter/url/https/twitter.com/JohannesBGruber.svg?style=social&label=Follow%20%40JohannesBGruber)](https://twitter.com/JohannesBGruber)
<!-- badges: end -->

The goal of crowdtangler is to provide easy access to the [CrowdTangle API](https://github.com/CrowdTangle/API).

## Installation

`crowdtangler` is not on [CRAN](https://CRAN.R-project.org) yet.
Install via `remotes` (first install `remotes` via `install.packages("remotes")`:

``` r
remotes::install_github("JBGruber/crowdtangler")
```

## Authentication

Go to your CrowdTangle account and get your token. 
That's all you need to use the functions in this package.
For convenience, you can save your token using a dedicated function:

```{r auth, eval=FALSE}
library(crowdtangler)
ct_auth(token = "XXXxxxXXX")
```

Select where you want to save your token in the interactive menu.
From here on, whenever you load the package, your token will be there.

## Check your lists

Usually you want to do stuff with the lists you created on CrowdTangle.
In the API this works using the list's ID.
To get the IDs of all lists in your account, call:

```{r lists, eval=FALSE}
lists_df <- ct_getlists()
```

## Download leaderboard

```{r include=FALSE}
library(crowdtangler)
```

```{r leaderboard, eval=FALSE}
leaderboard <- ct_leaderboard(
  list = "1543877", # will only work if list is in your account
  count = 10,
  start = "2021-09-24T22:00:00",
  end = "2021-09-25T22:00:00"
)
leaderboard
#> # A tibble: 10 × 31
#>    accout_id accout_name            accout_handle accout_profileI… accout_subscrib…
#>        <int> <chr>                  <chr>         <chr>                       <int>
#>  1   1555176 Alice Weidel           aliceweidel   https://sconten…           386348
#>  2    445848 Karl Lauterbach        Karl.Lauterb… https://sconten…            82031
#>  3   1295156 Armin Laschet          ArminLaschet  https://sconten…            54745
#>  4    471941 Annalena Baerbock      abaerbock     https://sconten…            79141
#>  5    627952 Prof. Dr. Jörg Meuthen Prof.Dr.Joer… https://sconten…           149164
#>  6    449338 Olaf Scholz            olafscholz    https://sconten…            46418
#>  7   2342315 Tino Chrupalla         TinoAfD       https://sconten…            28957
#>  8    401961 Beatrix von Storch     BeatrixVonSt… https://sconten…           107326
#>  9   2232965 Stephan Brandner, MdB  stBrandner    https://sconten…            25935
#> 10    385506 Martin Sonneborn       MartinSonneb… https://sconten…           310728
#> # … with 26 more variables: accout_url <chr>, accout_platform <chr>,
#> #   accout_platformId <chr>, accout_accountType <chr>,
#> #   accout_pageAdminTopCountry <chr>, accout_pageDescription <chr>,
#> #   accout_pageCreatedDate <chr>, accout_pageCategory <chr>,
#> #   accout_verified <lgl>, summary_loveCount <int>,
#> #   summary_threePlusMinuteVideoCount <int>,
#> #   summary_totalInteractionCount <int>, summary_wowCount <int>, …
```


## Download posts

```{r posts, eval=FALSE}
posts <- ct_posts(
  list = "1543877", # will only work if list is in your account
  count = 10,
  start = "2021-09-24T22:00:00",
  end = "2021-09-25T22:00:00",
  parse = TRUE
)
posts
#> # A tibble: 10 × 36
#>    accout_id accout_name     accout_handle   accout_profileIma… accout_subscrib…
#>        <int> <chr>           <chr>           <chr>                         <int>
#>  1    468446 Kai Wegner      kai.wegner2.0   https://scontent-…             6706
#>  2    444484 Bodo Ramelow    bodo.ramelow    https://scontent-…            45472
#>  3   1517959 Sarah Ryglewski sarah.ryglewski https://scontent-…             2952
#>  4    453450 Marco Bülow     marco.buelow    https://scontent-…            16101
#>  5   1379083 Michael Theurer michael.theurer https://scontent-…            27729
#>  6   1295156 Armin Laschet   ArminLaschet    https://scontent-…            54745
#>  7    449338 Olaf Scholz     olafscholz      https://scontent-…            46418
#>  8    444689 Dirk Wiese      dirkwiesespd    https://scontent-…             4532
#>  9    453906 Emmi Zeulner    ZeulnerEmmi     https://scontent-…             6035
#> 10    444689 Dirk Wiese      dirkwiesespd    https://scontent-…             4532
#> # … with 31 more variables: accout_url <chr>, accout_platform <chr>,
#> #   accout_platformId <chr>, accout_accountType <chr>,
#> #   accout_pageAdminTopCountry <chr>, accout_pageDescription <chr>,
#> #   accout_pageCreatedDate <chr>, accout_pageCategory <chr>,
#> #   accout_verified <lgl>, platformId <chr>, platform <chr>, date <chr>,
#> #   updated <chr>, type <chr>, message <chr>, link <chr>, postUrl <chr>,
#> #   subscriberCount <int>, score <dbl>, videoLengthMS <int>, …
```

